Appendix to ``Automated Assessment of Residual Plots with Computer Vision Models''

### 2025-06-17 appendix.tex
Fix heading issue in appendix

\subsection{Neural Network Layers Used in the
Study}\label{neural-network-layers-used-in-the-study}

@@

\subsubsection{Dense Layer}\label{dense-layer}

@@

\subsubsection{ReLu Layer}\label{relu-layer}

@@

\subsubsection{Convolutional Layer}\label{convolutional-layer}

@@

\subsubsection{Pooling Layer}\label{pooling-layer}

@@

\subsubsection{Global Pooling Layer}\label{global-pooling-layer}

@@

\subsubsection{Batch Normalization
Layer}\label{batch-normalization-layer}

@@

\subsubsection{Dropout Layer}\label{dropout-layer}

>>>>

\section{Neural Network Layers Used in the
Study}\label{neural-network-layers-used-in-the-study}

@@

\subsection{Dense Layer}\label{dense-layer}

@@

\subsection{ReLu Layer}\label{relu-layer}

@@

\subsection{Convolutional Layer}\label{convolutional-layer}

@@

\subsection{Pooling Layer}\label{pooling-layer}

@@

\subsection{Global Pooling Layer}\label{global-pooling-layer}

@@

\subsection{Batch Normalization Layer}\label{batch-normalization-layer}

@@

\subsection{Dropout Layer}\label{dropout-layer}
